% Created 2020-02-01 Sat 20:48
% Intended LaTeX compiler: pdflatex
\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{mycv}
\usepackage{datetime}
\hypersetup{colorlinks=true, urlcolor={url-gray}}
\usepackage{enumitem}
\usepackage{tabularx}
\setlist{leftmargin=0.25in,nosep}
\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}
\setlength{\parskip}{-0.05cm}
\author{Adam Massmann}
\date{\today}
\title{Adam Massmann's CV}
\hypersetup{
  pdfauthor={Adam Massmann},
  pdftitle={Adam Massmann's CV},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 26.1 (Org mode 9.1.9)},
  pdflang={English}}

% Use Biblatex
\input{biblatex-config.tex}

\addbibresource{massmann-papers.bib}


\begin{document}

\resheader{Adam Massmann}{http://www.columbia.edu/~akm2203/}{New York,
  NY}{akm2203@columbia.edu}{+1 206 919 1364}

\section{Interests}
\label{sec:org055839b}

human-land-atmosphere interaction,computer tools for blending physical models and data

\section{Education}
\label{sec:orge43ed1a}

\begin{center}
  \begin{tabularx}{\textwidth}{lXr}
    \textbf{Ph.D. in Environmental Engineering, Columbia University} &  & \emph{in progress, expected 2021}\\
    \textbf{M.S. in Atmospheric Science, University at Albany} &  & \emph{2016}\\
    \textbf{B.S. in Civil Engineering, University of Washington} &  & \emph{cum laude, 2014}\\
  \end{tabularx}
\end{center}

\section{Research experience}
\label{sec:orgda87656}

\begin{center}
  \begin{tabularx}{\textwidth}{lXr}
    \textbf{Graduate Research Assistant} &  & \emph{Sept. 2016 - Present}\\
    \emph{Environmental Engineering} &  & \emph{Columbia University}\\
  \end{tabularx}
\end{center}

\begin{center}
  \begin{tabularx}{\textwidth}{lXr}
    \textbf{Graduate Research Assistant} &  & \emph{May. 2015 - Aug. 2016}\\
    \emph{Atmospheric and Environmental Sciences} &  & \emph{University at Albany}\\
  \end{tabularx}
\end{center}

\begin{center}
  \begin{tabularx}{\textwidth}{lXr}
    \textbf{Undergraduate Research Assistant} &  & \emph{Nov. 2012 - Aug. 2014}\\
    \emph{Civil and Environmental Engineering} &  & \emph{University of Washington}\\
  \end{tabularx}
\end{center}

\section{Teaching experience}
\label{sec:org8ff7472}

\begin{center}
  \begin{tabularx}{\textwidth}{lXr}
    \textbf{Graduate Teaching Assistant} &  & \emph{Aug. 2014 - May 2015}\\
    \emph{Atmospheric and Environmental Sciences} &  & \emph{University at Albany}\\
  \end{tabularx}
\end{center}
\begin{itemize}
\item \emph{Introduction to Environmental Science; Surface Hydrology and Hydrometeorology}
\end{itemize}

\section{Awards, fellowships and scholarships}
\label{sec:org83586fe}

\begin{itemize}
\item \textbf{\href{https://ctl.columbia.edu/graduate-instructors/opportunities-for-graduate-students/lead-teaching-fellows/}{Lead Teaching Fellow}}, Columbia University, 2019-Present
\item \textbf{Presidential Fellow}, Columbia University, 2019-Present
\item \textbf{PI, XSEDE Startup Allocation:} "A moist static energy approach to
  understanding wet and dry season transitions in the Amazon
  rainforest," 2016-2018
\item \textbf{NSF Graduate Research Fellowship Program}, 2015-2019
\item \textbf{AMS Student Travel Grant}, 16th Conference on Mountain Meteorology, 2014
\item \textbf{Annual Dean's List}, University of Washington, 2012-2014
\item \textbf{Ruth and Richard Meese Endowed Scholarship}, Department of Civil Engineering, University of Washington, 2013-2014
\item \textbf{Mary Gates Research Scholarship},  University of Washington, 2013
\item \textbf{John Arthur Elliot Endowed Scholarship}, Department of Civil
  Engineering,  University of Washington, 2013
\end{itemize}

\section{Technical skills}
\label{sec:orgf5d7790}

\subsection{Software}
\label{sec:org363bbc4}
\begin{itemize}
\item \textbf{Languages} : Haskell, F\#, Scheme, Python
\item \textbf{Free Software Contributions} : \href{https://github.com/DougBurke/hvega}{hvega};  \href{https://github.com/haskell-numerics/hmatrix}{hmatrix}; \href{https://github.com/trevorkeenan/FLUXNET\_citations}{FLUXNETcitations}; \href{https://www.gnu.org/software/guix/}{GNU Guix}
\end{itemize}

\subsection{Field observations and hardware}
\label{sec:orgad8ef21}
\begin{itemize}
\item \emph{Campbell Scientific dataloggers, InterMet radiosondes, PARSIVEL disdrometers,}
  \emph{METEK Micro Rain Radars, HOBO dataloggers, iButton chips, Raspberry Pi boards,}
  \emph{eddy-covariance turbulent flux estimation.}
\end{itemize}
\subsection{Construction}
\label{sec:org208f43c}
\begin{itemize}
\item \emph{Shaft, steel and concrete construction; tractor operation; manlift operation.}
\end{itemize}

\newpage

\section{Field experience}
\label{sec:org1dedf6e}
\begin{itemize}
\item CCOPE-2015 Field Campaign (2015, \href{http://www.atmos.albany.edu/student/massmann/ccope.html}{ccope.html}), Chile: \emph{field operations lead}
\item Pre-OLYMPEX Field Campaign (2014), Washington State: \emph{site
    design, testing and deployment (snow depth)}
\item Snoqualmie Pass Snow Energy Balance Research Site (2013-2014),
  Washington State: \\
  \emph{primary field technician; software design
    for data archival and quality control}
\end{itemize}

\section{Additional education}
\label{sec:org6506402}
\begin{itemize}
\item \emph{Innovative Teaching Summer Institute}, Columbia University Center
  for Teaching and Learning, June 2016
\item \emph{Implicit Bias Workshop}, Columbia University, March 15, 2019
\item \emph{Fluid Dynamics of Sustainability and the Environment}, Department
  of Applied Mathematics and Theoretical Physics, University of
  Cambridge, August 2016
\end{itemize}

\section{Service and extracurriculars}
\label{sec:org4d93625}

\begin{itemize}
\item \href{https://zuckermaninstitute.columbia.edu/stem-starters}{STEM Starters Outreach}, Education Lab, Columbia University, Sept. 2019
\item Volunteer, \emph{New York Scientific Data Summit}; June, 2019
\item Essay reader: \emph{Washington State Opportunity Scholarship}; Mar. 2019
\item 6th Grade Science Interviewee; Realm School (Berkeley, CA); Sept. 2016
\item UAlbany Weather Camp Volunteer; University at Albany; Aug. 2016
\item Science Outreach to Voorheesville HS students; University at Albany; Mar. 2016
\item Science Outreach at Liceo Mariano Latorre; Curanilahue, Chile; Aug. 2015
\item Engineering Discovery Day; University of Washington; 2013, 2014
\item Volunteer Board Member, Northwest Youth Water Polo, Oct. 2013 - Aug. 2014
\item Reviewer for \emph{Geophysical Research Letters}, \emph{Journal of Applied
    Meteorology and Climatology}, \emph{Journal of Climate}, \emph{Journal of
    Hydrometeorology}, \emph{Water Resources Research}, \emph{Weather and
    Forecasting}
\end{itemize}

% Publications
\boldname{Massmann}{Adam}{K}
\nocite{*}
\printbibheading
\bibbycategory

\end{document}